\chapter*{Author's Achievements}\label{chapter_author_biblio}
\addcontentsline{toc}{chapter}{Author's Achievements}


\noindent \textbf{Journal papers focused directly on the dissertation`s subject}:
\begin{itemize}[nosep]
\item \bibentry{polyjet_susp_coupler}
\item \bibentry{mwcl_cascaded_multipex}
\item \bibentry{tmtt_crosscoupled_DF}
\item \bibentry{mwcl_band_reject}
\item \bibentry{jmwt_imp_tranforming}
\item \bibentry{jiee_imp_tranf_balun}
\item \bibentry{mwcl_dcrlh}
\item \bibentry{jemwa_pseudo-highpass}
\item \bibentry{tmtt_right_left}
\item \bibentry{mwcl_tandem}
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Journal papers not related to the dissertation's subject}:
\begin{itemize}[nosep]
%\item \bibentry{tmtt_aerosol}
\item I. Piekarz, J. Sorocki, M. T. Craton, K. Wincza, S. Gruszczynski, and J. Papapolymerou,
“Applications of aerosol jet 3D printing with conductive and non-conductive inks for the realization of mm-wave circuits,” \textit{in preparation}, 2018
%\item \bibentry{mwcl_three_section_diff}
\item I. Piekarz, J. Sorocki, K. Janisz, K. Wincza, and S. Gruszczynski, “Wideband three-section
symmetrical coupled-line directional coupler operating in differential mode,” submitted to \textit{IEEE Microwave and Wireless Components Letters}, 2018
%\item \bibentry{mwcl_tandem_three}
%\item \bibentry{sensors_two_wire}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Liquids permittivity measurement using two-wire transmission line sensor,” submitted to \textit{IEEE Sensors Journal}, 2018
%\item \bibentry{tie_vector}
\item K. Staszek, I. Piekarz, J. Sorocki, S. Koryciak, K. Wincza, and S. Gruszczynski, “Low-cost
microwave vector system for liquid properties monitoring,” \textit{IEEE Transactions on Industrial Electronics}, vol. 65, no. 2, pp. 1665–1674, Feb. 2018
%\item \bibentry{tmtt_coupled_sensor}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Microwave sensors for dielectric samples measurement based on coupled-line section,” \textit{IEEE Transactions on Microwave Theory and Techniqes}, vol. 65, no. 5, pp. 1615–1631, May 2017
%\item \bibentry{jemwa_leaky}
\item I. Slomian, J. Sorocki, S. Gruszczynski, and K. Wincza, “Composite right-left handed leaky-wave antenna with adjustable radiation bandwidth,” \textit{Journal of ElectromagneticWaves and Applications}, vol. 30, no. 8, pp. 1054–1063, 2016
%\item \bibentry{jiee_imp_tranf_balun}
\item J. Sorocki, I. Piekarz, P. Kaminski, K. Wincza, and S. Gruszczynski, “Broadband balun circuits composed of impedance transforming directional couplers and LH transmission-line sections,” \textit{International Journal of Microwave and Wireless Technologies}, vol. 6, no. 3, pp. 147–150, 2016
%\item \bibentry{ijmwt_two_section}
\item J. Sorocki, K. Staszek, I. Piekarz, K. Wincza, and S. Gruszczynski, “Application of RH and LH sections for reduction of coupling coefficients in two-section asymmetric directional couplers,” \textit{International Journal of Microwave and Wireless Technologies}, vol. 8, pp. 559–565, May 2016
%\item \bibentry{sensors_coupled}
\item I. Piekarz, J. Sorocki, K.Wincza, and S. Gruszczynski, “Coupled-line sensor with marchand balun as RF system for dielectric sample detection,” \textit{IEEE Sensors Journal}, vol. 16, no. 1, pp. 88–96, Jan. 2016
%\item \bibentry{mwcl_balun}
\item I. Piekarz, J. Sorocki, S. Gruszczynski, and K. Wincza, “Input match and output balance
improvement of marchand balun with connecting line,” \textit{IEEE Microwave and Wireless
Components Letters}, vol. 24, no. 10, pp. 683–685, Oct. 2014
%\item \bibentry{rfmcae_modelling_coupled}
\item I. Piekarz, J. Sorocki, S. Gruszczynski, and K. Wincza, “Modeling and performance improvement of folded coupled lines in miniaturized quasi-lumped directional couplers,” \textit{International Journal of RF and Microwave Computer-Aided Engineering}, vol. 25, no. 1, pp. 1–9, Jan. 2015
%\item \bibentry{rfmcae_magic-T}
\item J. Sorocki, I. Piekarz, K. Wincza, and S. Gruszczynski, “Broadband magic-Ts with the use
of coupled-line directional couplers and left-handed transmission line sections,” \textit{International Journal of RF and Microwave Computer-Aided Engineering}, vol. 24, no. 4, pp. 513–521, Jul. 2014
%\item \bibentry{map_reduced_couppling}
\item J. Sorocki, K. Staszek, I. Piekarz, K. Wincza, and S. Gruszczynski, “Directional couplers
with reduced coupling requirements as a connection of coupled-line sections and left-handed
transmission lines,” \textit{IET Microwaves, Antennas and Propagation}, vol. 8, no. 8, pp. 580–588, Jun. 2014
%\item \bibentry{rfmcae_rat-race}
\item J. Sorocki, I. Piekarz, K. Wincza, and S. Gruszczynski, “Bandwidth improvement of rat-race
couplers having left-handed transmission-line sections,” \textit{International Journal of RF and
Microwave Computer-Aided Engineering}, vol. 24, no. 3, pp. 341–347, May 2014
%\item \bibentry{motl_ltcc}
\item I. Piekarz, J. Sorocki, K. Wincza, S. Gruszczynski, J. Muller, and T. Welker, “Miniaturized
quasi-lumped coupled-line single-section directional coupler designed in multilayer LTCC
technology,” \textit{Microwave and Optical Technology Letters}, vol. 55, no. 6, pp. 1401–1405, Jun. 2013
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Conference communicates focused directly on the dissertation's subject}:
\begin{itemize}[nosep]
\item \bibentry{mikon_low-loss_distributed}
\item \bibentry{ectc_electrify}
\item \bibentry{ectc_df}
\item \bibentry{iceese_3D_graphene}
\item \bibentry{mms_low-loss_wideband}
\item \bibentry{rws_imp_tuner}
\item \bibentry{mikon_cascaded_DF}
\item \bibentry{isap_miniaturized_DF}
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Conference communicates not related to the dissertation's subject}:
\begin{itemize}[nosep]
%\item \bibentry{eumw_aerosol}
\item M. T. Craton, J. Sorocki, I. Piekarz, S. Gruszczynski, K. Wincza, and J. Papapolymerou,
“Realization of fully 3D printed W-band bandpass filters using aerosol jet printing technology,”
submitted to \textit{European Microwave Week (EuMW 2018)}, Madrid, Spain, Sep. 2018
%\item \bibentry{mikon_coupled_liquid}
\item \bibentry{apwc_absorber}
\item \bibentry{iceaa_magnetic}
\item I. Slomian, J. Sorocki, I. Piekarz, K. Wincza, and S. Gruszczynski, “Aperture-coupled microstrip antenna integrated with PET-G dielectric lens,” in \textit{International Conference on Electromagnetics in Advanced Applications (ICEAA 2018)}, Cartagena de Indias, Colombia, Sep. 2018.
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Coupled-line sensor setup with liquids and solids permittivity sensing capability developed with the use of 3D printing technology,” in \textit{International Conference on Microwave, Radar and Wireless Communications (MIKON 2018)}, Poznan, Poland, May 2018
%\item \bibentry{iceese_multi}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Multi-coupled-line microwave sensors for dielectric sample permittivity change detection,” in \textit{International Conference on Electrical, Electronics and System Engineering (ICEESE 2017)}, Kanazawa, Japan, Nov. 2017, pp. 48–51
%\item \bibentry{comite_antenna}
\item J. Sorocki, I. Piekarz, S. Gruszczynski, and K. Wincza, “Approach to the design of wideband
antenna arrays with reduced coupling between elements,” in \textit{Conference on Microwave Techniques
(COMITE 2017)}, Brno, Czech Republik, Apr. 2017
%\item \bibentry{comite_sensor}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Low-cost planar coupled-line sensor for permittivity measurement of low-loss dielectric materials in a wide frequency range,” in \textit{Conference on Microwave Techniques (COMITE 2017)}, Brno, Czech Republik, Apr. 2017
%\item \bibentry{comite_system}
\item I. Piekarz, K. Janisz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Two-port measurement
system with coupled-line sensor for detection of material permittivity change,” in \textit{Conference on Microwave Techniques (COMITE 2017)}, Brno, Czech Republik, Apr. 2017
%\item \bibentry{rws_rat}
\item I. Piekarz, J. Sorocki, K.Wincza, and S. Gruszczynski, “Rat-race directional couplers operating in differential mode,” in \textit{Radio and Wireless Symposium (RWS 2017)}, Phoenix, AZ, USA, Jan. 2017
%\item \bibentry{msmw_compact}
\item J. Sorocki, I. Piekarz, S. Gruszczynski, and K. Wincza, “Compact microstrip coupled-line
directional coupler realized in thick-film technology,” in \textit{International Kharkiv Symposium on Physics and Engineering of Microwaves, Millimeter and Submillimeter Waves (MSMW 2016)}, Kharkiv, Ukraine, Jun. 2016
%\item \bibentry{msmw_differentialy}
\item J. Sorocki, I. Piekarz, K. Wincza, and S. Gruszczynski, “Differentialy excited coupled-line
sensor for small dielectric samples detection,” in \textit{International Kharkiv Symposium on Physics and Engineering of Microwaves, Millimeter and Submillimeter Waves (MSMW 2016)}, Kharkiv,
Ukraine, Jun. 2016
%\item \bibentry{msmw_miniaturized}
\item J. Sorocki, I. Piekarz, K. Wincza, and S. Gruszczynski, “Miniaturized microstrip marchand balun and coupled-line section as microwave sensor for dielectric material detection,” in \textit{International Kharkiv Symposium on Physics and Engineering of Microwaves, Millimeter and Submillimeter Waves (MSMW 2016)}, Kharkiv, Ukraine, Jun. 2016
%\item \bibentry{msmw_sensitivity}
\item Piekarz, J. Sorocki, S. Gruszczynski, and K. Wincza, “Sensitivity investigation of coupled-line microwave sensor on dielectric Material-Under-Test,” in \textit{International Kharkiv Symposium on Physics and Engineering of Microwaves, Millimeter and Submillimeter Waves (MSMW 2016)}, Kharkiv, Ukraine, Jun. 2016
%\item \bibentry{msmw_simplified}
\item I. Piekarz, J. Sorocki, K.Wincza, and S. Gruszczynski, “Simplified three-strip coupled-line section as microwave sensor for dielectric materials measurement,” in \textit{International Kharkiv Symposium on Physics and Engineering of Microwaves, Millimeter and Submillimeter Waves (MSMW 2016)}, Kharkiv, Ukraine, Jun. 2016
%\item \bibentry{msmw_calibration}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Calibration method of microwave
measurement system for dielectric samples detection,” in\textit{ International Kharkiv Symposium on Physics and Engineering of Microwaves, Millimeter and Submillimeter Waves (MSMW 2016)},
Kharkiv, Ukraine, Jun. 2016
%\item \bibentry{mikon_compensated}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Miniaturized compensated quasi-lumped wideband Marchand balun,” in \textit{International Conference on Microwave, Radar and Wireless Communications (MIKON 2016)}, Krakow, Poland, May 2016
%\item \bibentry{rws_effective}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Effective permittivity measurement with the use of coupled-line section sensor,” in \textit{Radio and Wireless Symposium (RWS 2016)}, Austin, TX, United States of America, Jan. 2016
%\item \bibentry{isap_wideband}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Wideband marchand balun and bow-tie antenna for sensor applications,” in \textit{International Symposium on Antennas and Propagation (ISAP 2015)}, Hobart, Australia, Nov. 2015
%\item \bibentry{isap_leaky}
\item S. Gruszczynski, A. Rydosz, J. Sorocki, I. Slomian, P. Kaminski, and K. Wincza, “Leaky-wave
antenna in multilayer structure for sensor applications,” in \textit{International Symposium on Antennas and Propagation (ISAP 2015}), Hobart, Australia, Nov. 2015
%\item \bibentry{wamicon_slot}
\item J. Sorocki, I. Piekarz, I. Slomian, K. Wincza, and S. Gruszczynski, “Approach to the design
of slot-coupled-line directional couplers,” in \textit{Wireless and Microwave Technology Conference (WAMICON 2015)}, Cocoa Beach, FL, United States of America, Apr. 2015
%\item \bibentry{wamicon_marchand}
\item I. Piekarz, J. Sorocki, I. Slomian, K. Wincza, and S. Gruszczynski, “Compact single-layer
microstrip marchand type balun,” in \textit{Wireless and Microwave Technology Conference (WAMICON
2015)}, Cocoa Beach, FL, United States of America, Apr. 2015
%\item \bibentry{mms_magicT}
\item J. Sorocki, I. Piekarz, I. Slomian, K. Staszek, K. Wincza, and S. Gruszczynski,
“Bandwidth-enhanced single-layer 3-dB tandem directional coupler as magic-T network,” in
\textit{Mediterranean Microwave Symposium (MMS 2014)}, Marrakech, Morocco, Dec. 2014
%\item \bibentry{mms_marchand}
\item I. Piekarz, J. Sorocki, I. Slomian, K. Staszek, K. Wincza, and S. Gruszczynski, “Marchand
balun with connecting segment designed with the use of multi-technique compensation,” in
\textit{Mediterranean Microwave Symposium (MMS 2014)}, Marrakech, Morocco, Dec. 2014
%\item \bibentry{mms_lattice}
\item I. Slomian, K. Staszek, I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Dual polarized two-port antenna lattice,” in \textit{Mediterranean Microwave Symposium (MMS 2014)}, Marrakech, Morocco, Dec. 2014
%\item \bibentry{isap_leaky_meta}
\item S. Gruszczynski, A. Rydosz, J. Sorocki, I. Slomian, and K. Wincza, “Leaky-wave antenna
with modified metamaterial unit cell for narrowing beam steering bandwidth,” in \textit{International Symposium on Antennas and Propagation (ISAP 2014)}, Kaohsiung, Taiwan, Dec. 2014
%\item \bibentry{mikon_magicT}
\item J. Sorocki, I. Piekarz, I. Slomian, S. Gruszczynski, and K. Wincza, “Single-layer coupled-line magic-ts utilizing left-handed transmission line sections,” in \textit{International Conference on Microwave, Radar and Wireless Communications (MIKON 2014}), Gdansk, Poland, May 2014
%\item \bibentry{mikon_array24}
\item I. Slomian, P. Kaminski, J. Sorocki, I. Piekarz, K. Wincza, and S. Gruszczynski, “Multi-beam and multi-range antenna array for 24 GHz radar applications,” in \textit{International Conference on Microwave, Radar and Wireless Communications (MIKON 2014)}, Gdansk, Poland, May 2014
%\item \bibentry{crimico_four}
\item I. Piekarz, J. Sorocki, I. Slomian, M. Sloma, P. Kaminski, K. Wincza, and S. Gruszczynski,
“Miniaturized coupled-line directional coupler designed with the use of photoimageable thick-film
technology,” in \textit{International Crimean Conference Microwave and Telecommunication Technology (CriMiCo 2013), Sevastopo}l, Ukraine, Sep. 2013
%\item \bibentry{crimico_antenna}
\item P. Sanz, I. Slomian, I. Piekarz, J. Sorocki, P. Kaminski, K. Wincza, and S. Gruszczynski,
“Four-beam antena array for 24 GHz applications fed by 4x4 Butler matrix,” in \textit{International Crimean Conference Microwave and Telecommunication Technology (CriMiCo 2013)}, Sevastopol,
Ukraine, Sep. 2013
%\item \bibentry{imoc_antenna}
\item I. Slomian, J. Sorocki, P. Kaminski, A. Rydosz, K. Wincza, and S. Gruszczynski, “Broadband 4 x 4 microstrip antenna array utilizing slot-coupled power dividers,” in \textit{International Microwave and Optoelectronics Conference (IMOC 2013)}, Rio de Janeiro, Brasil, Aug. 2013
%\item \bibentry{telfor_asymmetric}
\item I. Piekarz and J. Sorocki, “Asymmetric coupled-line single-section directional coupler with
equalized inductive and capacitive coupling coefficients,” in \textit{Telecommunications Forum (TELFOR 2012)}, Belgrade, Serbia, Nov. 2012
%\item \bibentry{telfor_ltcc}
\item I. Piekarz, J. Sorocki, K. Wincza, and S. Gruszczynski, “Meandered coupled-line single-section directional coupler utilizing multilayer LTCC technology,” in \textit{Telecommunications Forum (TELFOR 2012)}, Belgrade, Serbia, Nov. 2012
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Leadership of research projects}:
\begin{itemize}[nosep]
\item Research project awarded by the National Science Centre under \textit{Etiuda} 4 program, entitled "Low-loss microwave circuits in strip transmission line technique. Analysis, design and experimental investigations". ID project number 2016/20/T/ST7/00202. Project granted for 2016--2018.
\item Research project awarded by the National Science Centre under \textit{Preludium} 7 program, entitled "Investigation on high-performance low-loss microwave directional filters for application in high-power systems". ID project number 2014/13/N/ST7/01961. Project granted for 2015--2018.
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Participation in research projects}:
\begin{itemize}[nosep]
\item Research Project granted by the National Centre for Research and Developement under the \textit{POIR} program, entitled "The use of tropospheric communication to increase the range of unmanned aerial vehicles - BSP" -- investigator. ID project~number POIR.01.01.01-00-0070/17. Project~granted for 2017--2019.
\item Research Project granted by the National Centre for Research and Developement under the \textit{Lider} program, entitled "Sensor nanostructures for use in portable breath analyzers" -- investigator. ID project~number LIDER/252/L-6/NCBR/2015. Project~granted for 2016--2019.
\item Research Project awarded by the National Centre for Research and Developement under the \textit{POIR} program, entitled "Air traffic control system of the new generation ADS-B / MLAT" -- investigator. ID project~number POIR.01.01.01-00-0169/15. Project~granted for 2016--2017.
\item Research Project granted by the Ministry of Science and Higher Education under the \textit{Iuventus Plus} Program (second edition), entitled, "Investigations on realization of low-loss passive microwave power division/summation circuits for applications in high-power microwave amplifiers" -- investigator. ID project number 0510/IP2/2015/73. Project granted for 2015--2019.
\item Research Project granted by the National Science Centre under the \textit{Sonata Bis} Program, entitled "Research on the transmission lines having negative phase velocity and their application to novel microwave circuits" -- investigator. ID project~number 2011/01/D/ST7/00789. Project~granted for 2011--2015.
\item Research Project granted by the Ministry of Science and Higher Education, entitled, "Miniaturized microwave broadband directional couplers designed with the use of quasi-lumped technique" -- investigator. ID project number 4999/B/T02/2011/40. Project granted for 2011--2013.
\item Research Project granted by the Ministry of Science and Higher Education under the \textit{Iuventus Plus} Program (second edition), entitled, "Broadband microwave directional couplers realized in structures having decreased available coupling coefficient -- synthesis methods, design and application to novel microwave electronics" -- investigator. ID project number 0604/IP2/2011/71. Project granted for 2011--2015.
\item Research Project granted by the National Centre for Research and Developement under the \textit{Lider} program, entitled "Miniature integrated radar devices for industrial applications and anti-collision radars" -- investigator. ID project~number 4999/B/T02/2011/40. Project~granted for 2012--2013.
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Research visits, internships, training courses}:
\begin{itemize}[nosep]
\item 2017.05-11 - Michigan State University, East Lansing, MI, United States of America – half-year research visit within NCN Etiuda program, cooperation with prof. I. Papapolimerou on the design and manufacturing of microwave circuits using additive 3D manufacturing technologies.
\item 2015.08 - Wageningen University, Wageningen, Netherlands – 2-week soft-skills and entrepreneurship course within ‘Transformation.doc’ organized by the Polish Ministry of Science and Higher Education for Young Scientists.
\item 2012-2013 - AGH University of Science and Technology, Krakow, Poland – Research Assistant internship in High Frequency Electronics and Microwave Technique Research Group under prof. S. Gruszczynski supervision.
\item 2012.04-0.9 - Ilmenau University of Technology, Ilmenau, Germany – half-year stay within LLP EASMUS student exchange program, cooperation with prof. J. Müeller on the design and manufacturing of microwave circuits in LTCC (Low Temperature Co fired Ceramics) technology.
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Active participation in scientific events}:
\begin{itemize}[nosep]
\item 68\textsuperscript{th} IEEE Electronic Components and Technology Conference ECTC'18, 29 May - 01 Jun. 2018, San Diego, CA, USA.
\item 22\textsuperscript{nd} International Conference on Microwaves, Radar, and Wireless Communications MIKON'18, 15-17 May 2018, Poznan, Poland.
\item 3\textsuperscript{rd} International Conference on Electrical, Electronics and System Engineering ICEESE'17, 09-10 Nov. 2017, Kanazawa, Japan.
\item Microwave and Radio Electronics Week MAREW'17 (18\textsuperscript{th} Conference on Microwave Techniques COMITE'17), 19-21 Apr. 2018, Brno, Czech Republic.
\item 11\textsuperscript{th} IEEE Radio and Wireless Week RWW'17, 15-18 Jan. 2017, Phoenix, AZ, USA. %11
\item 9\textsuperscript{th} International Kharkiv Symposium on Physics and Engineering of Microwaves, Millimeter and Submillimeter Waves MSMW'16, 20-24 Jun. 2016, Kharkiv, Ukraine.
\item XXXVIIIth IEEE-SPIE Joint Symposium Wilga 2016, 30 May. – 6 Jun. 2016, Wilga, Poland.
\item 21\textsuperscript{th} International Conference on Microwave, Radar and Wireless Communications MIKON'16, 9-11 May 2016, Krakow, Poland.
\item 10\textsuperscript{th} IEEE Radio and Wireless Week RWW'16, 24-27 Jan. 2016, Austin, TX, USA. %10
\item International Symposium on Antennas and Propagation ISAP'15, 9-12 Nov. 2015, Hobart, Tasmania, Australia.
\item 16\textsuperscript{th} IEEE MTT-S Wireless and Microwave Technology Conference WAMICON'15, 13-15 Apr. 2015, Cocoa Beach, FL, USA.
\item 14\textsuperscript{th} Mediterranean Microwave Symposium MMS'14, 12-14 Dec. 2014, Marrakech, Morocco.
\item 24\textsuperscript{th} International Travelling Summer School on Microwaves and Lightwaves, 5-11 Jul. 2014, Copenhagen, Denmark.
\item 20\textsuperscript{th} International Conference on Microwaves, Radar, and Wireless Communications MIKON'14, 16-18 Jun. 2014, Gdansk, Poland.
\item 23\textsuperscript{rd} International Crimean Conference Microwave and Telecommunication Technology CriMiCo'13, 8-14 Sep. 2013, Sevastopol, Ukraine. %23
\item 20\textsuperscript{th} Telecommunications Forum TELFOR'12, 20-22 Nov. 2012, Belgrade, Serbia.
\end{itemize}
\vspace*{1cm} %\vfill

\noindent \textbf{Prizes and Awards}:
\begin{itemize}[nosep]
\item Minister of Science and Higher Education scholarship for academic merits and outstanding achievements of Doctoral Researchers in 2015.
\item Rectors’s scholarship for the best Doctoral Students at AGH University of Science and Technology in 2013, 2014, 2015, 2016 and 2017,
\item Dean's Grants awarded in 2014, 2015, 2016, and 2017.
\end{itemize}
\vspace*{1cm} %\vfill

\cleardoublepage